Quality assurance of digital twins -- An experience report in the automotive industry

### 2022-12-13 manuscripts/paper-1/main.tex
Improving the literature review methodology

    \subsection{Research questions}

    What is the quality of digital twins? What is good quality? What is bad quality? What is the impact of good quality? What is impact of bad quality? What are typical quality issues? How to assess quality? ...

@@

    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:case})...

    \section{Literature review}
    \label{section:literature}

    Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...

    \subsection{Methodology}
    \label{section:liteature_methodology}

    How did we find existing literature?

    \begin{itemize}
        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (quality OR defect OR issue OR error)
        \item ("digital twin" OR "simulation model" OR "system model" OR "CAD model") AND (verification OR validation OR accreditation)
    \end{itemize}

>>>>

    \subsection{Research questions}
    \label{section:Research Questions}

    What is the quality of digital twins? 
    What is good quality?
    What is bad quality? 
    What is the impact of good quality? 
    What is impact of bad quality? W
    What are typical quality issues? 
    How to assess quality?

@@

    Literature review (see Section~\ref{section:literature}), case study (see Section~\ref{section:Research Questions})...

    \section{Literature review}
    \label{section:literature}
    Literature analysis was executed, to analyze current DT literature within the concept of digital twin quality. The analysis, especially focused on 
    how the digital twin quality is mentioned and assessed within the academic dissertations.

    Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...
    \subsection{Methodology}
    \label{section:liteature_methodology}

    Google Scholar(GS), Scopus(SCP) and Research Rabbit(RR) tools are used to fulfill our requirements for the literature review. 
    Since there is a great number of digital twin publications in academics, narrowing the research is necessary, so the following filtering has been done for all searches.
    \begin{itemize}
        \item Dissertations should be written in English and published in a journal.
        \item Paper is not older than 2018
    \end{itemize}

    Search terms appeared in the title/abstract with "digital twin quality";
    \begin{itemize}
        \item GS = allintitle: "digital twin quality" Return articles dated between 2018 - NOW  
        \item Scopus = TITLE-ABS-KEY ( "digital twin quality" )  AND  PUBYEAR  \textgreater  2018  AND  PUBYEAR  \textless  2023  AND  ( LIMIT-TO ( LANGUAGE ,  "English" ) ) 
    \end{itemize}

    GS gave five different results, while SCP gave 2 results.

    Further inspection has been done, and
